%-------------------------
% Resume in LaTeX
% Author: Dylan Connolly
% Compiled with: pdflatex connolly-resume.tex
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scaled=0.92]{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[margin=0.4in, top=0.3in, bottom=0.3in]{geometry}

% you will need to run mpm --install fontawesome5 for this document to compile
\usepackage{fontawesome5}

% icon commands
\newcommand{\iconEnvelope}{\faEnvelope\ }
\newcommand{\iconPhone}{\faPhone\ }
\newcommand{\iconGlobe}{\faGlobe\ }
\newcommand{\iconGithub}{\faGithub\ }
\newcommand{\iconLinkedin}{\faLinkedin\ }
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}

% colors
\definecolor{linkblue}{RGB}{0,51,102}

% hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkblue,
    urlcolor=linkblue,
    pdfborder={0 0 0}
}

% remove page numbers
\pagestyle{empty}

% section formatting
\titleformat{\section}
    {\large\bfseries\uppercase}
    {}
    {0em}
    {}
    [\titlerule]

\titlespacing*{\section}{0pt}{5pt}{3pt}

% custom commands
\newcommand{\resumeItem}[1]{\item{\small\linespread{0.90}\selectfont #1\par}}
\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r@{}}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-4pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r@{}}
        \textbf{#1} & \small{#2} \\
    \end{tabular*}\vspace{-4pt}
}

% list settings
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=12pt, topsep=0pt, itemsep=0pt, label=$\bullet$]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

% assert one page -- pdflatex exits non-zero if the resume grows past a page
\AtEndDocument{%
    \ifnum\value{page}>1
        \errmessage{ASSERT FAILED: resume is \thepage\space pages, expected 1}%
    \fi
}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\LARGE \textbf{Dylan Connolly}} \\[4pt]
    Tallahassee, FL \enspace$|$\enspace
    \iconEnvelope\href{mailto:dylan.t.con@gmail.com}{dylan.t.con@gmail.com} \enspace$|$\enspace
    \iconPhone(850) 376-8268 \\[2pt]
    \iconGlobe\href{https://dconn.dev}{dconn.dev} \enspace$|$\enspace
    \iconGithub\href{https://github.com/dylantcon}{github.com/dylantcon} \enspace$|$\enspace
    \iconLinkedin\href{https://linkedin.com/in/dylantcon}{linkedin.com/in/dylantcon}
\end{center}

%----------SUMMARY----------
\section{Summary}
Software engineer with experience in full-stack development, systems programming, and compiler construction. Proficient in C, C\#, Python, Java, and JavaScript/TypeScript. Built an EMR platform with REST API and RBAC, an OOXML presentation editor with a parity-tested rendering engine, a Lisp compiler with optimization passes, and Linux kernel modules. Skilled with relational databases (PostgreSQL, SQLite), web frameworks (Django, ASP.NET Core, React), and DevOps tools (Git, Linux).

%----------EDUCATION----------
\section{Education}

\resumeSubHeadingListStart
    \resumeSubheading
        {Florida State University}{Tallahassee, FL}
        {Bachelor of Science in Computer Science, Minor in Physics, Magna Cum Laude}{July 2026}
    \resumeItemListStart
        \resumeItem{GPA: 3.89/4.0 \enspace$\cdot$\enspace President's List: Spring 2025, Fall 2025 \enspace$\cdot$\enspace Dean's List: Fall 2023, Spring 2024, Spring 2026}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------EXPERIENCE----------
\section{Experience}

\resumeSubHeadingListStart
    \resumeSubheading
        {Software Engineering Intern}{Summer 2025}
        {Hanku (formerly CoderOgres)}{Tallahassee, FL}
    \resumeItemListStart
        \resumeItem{Developed Excudo as an internal tool for programmatic PowerPoint generation by reverse-engineering the OOXML standard, including undocumented animation and styling specifications, cutting slide-deck production time by \textbf{32\%} to accelerate curriculum workflows.}
        \resumeItem{Engineered a text-to-speech pipeline using \texttt{chatterbox-tts} and a custom markup language, generating lecture audio locally and replacing a commercial TTS service billed at roughly \$11 per hour of narration.}
        \resumeItem{Built \href{https://github.com/dylantcon/pydis}{PyDis}, a Python bytecode disassembler with side-by-side execution visualization, variable inspection, and I/O tracing for student debugging.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------PROJECTS----------
\section{Projects}

\resumeSubHeadingListStart

    \resumeProjectHeading
        {\href{https://github.com/dylantcon/excudo}{Excudo} $\vert$ \emph{Java 21, JavaFX, OOXML, Model Context Protocol, Python}}{Summer 2025 -- Present}
    \resumeItemListStart
        \resumeItem{Built a desktop presentation editor from scratch that reads and writes PowerPoint's native OOXML, evaluating the ECMA-376 guide formulas for all 187 preset shapes and calibrating text layout against PowerPoint's own PDF output.}
        \resumeItem{Verified rendering fidelity with an automated parity harness that scores every slide against a ground-truth PowerPoint corpus via SSIM, enforcing per-category thresholds and regression-ratcheting baselines in cross-platform CI.}
        \resumeItem{Replaced the traditional in-memory undo stack with a persistent per-slide command DAG that reconstructs edit history across restarts, and exposed the editor as an MCP server so an LLM client can inspect and edit live decks.}
    \resumeItemListEnd

    \resumeProjectHeading
        {\href{https://github.com/dylantcon/clinicore}{CliniCore} $\vert$ \emph{C\#, ASP.NET Core, Entity Framework, SQLite, .NET MAUI}}{Fall 2025}
    \resumeItemListStart
        \resumeItem{Architected EMR and practice management system with patient records, scheduling, clinical documentation, and prescription tracking across GUI and CLI interfaces.}
        \resumeItem{Implemented command pattern (CommandFactory, CommandInvoker) for unified state manipulation and undo/redo; designed medium-agnostic persistence layer supporting SQLite, in-memory, and REST API backends.}
        \resumeItem{Built complete REST API with role-based access control (RBAC) for all domain models; automated documentation with DocFX and GitHub Actions.}
    \resumeItemListEnd

    \resumeProjectHeading
        {\href{https://github.com/dylantcon/compiler-project}{Lisp Compiler} $\vert$ \emph{C, Lex/Flex, Yacc/Bison, GraphViz}}{Fall 2025}
    \resumeItemListStart
        \resumeItem{Built a complete compiler frontend for a Lisp-like language: lexical analysis, recursive descent parsing, AST generation, semantic analysis, and intermediate representation with control flow graph generation.}
        \resumeItem{Implemented optimization passes and generated DOT output for CFG visualization via GraphViz.}
    \resumeItemListEnd

    \resumeProjectHeading
        {\href{https://github.com/dylantcon/countertrak}{CounterTrak} $\vert$ \emph{Python, asyncio, aiohttp, Django, PostgreSQL, Docker}}{Spring 2025}
    \resumeItemListStart
        \resumeItem{Built a fully asynchronous \texttt{asyncio}/\texttt{aiohttp} ingestion server consuming Valve's Game State Integration payloads from many concurrent Counter-Strike 2 clients into PostgreSQL at up to ten snapshots per second per player; containerized it alongside the Django app as a two-service Docker Compose stack with production/demo parity and secrets kept out of the image.}
        \resumeItem{Designed a multi-tenant account system: users register and link Steam accounts through a Django interface, each issued a unique auth token embedded in a client-side GSI config that authenticates every payload against an in-memory token cache.}
        \resumeItem{Engineered a kill-attribution engine inferring per-weapon kills from game-state deltas, and computed player analytics over a BCNF-normalized schema using SQL window functions (\texttt{PERCENT\_RANK}, \texttt{LAG}) for percentile ranking and round-economy trends.}
    \resumeItemListEnd

    \resumeProjectHeading
        {\href{https://github.com/dylantcon/sysconf}{Sysconf} $\vert$ \emph{Python, TOML, Jinja2, NGINX, Certbot, Systemd}}{2026}
    \resumeItemListStart
        \resumeItem{Built an idempotent Linux provisioning tool: cross-distro package management, dotfile deployment, SSH hardening, Tailscale VPN, and automated NGINX + Let's Encrypt web-app deployment.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------SKILLS----------
\section{Skills}

\begin{itemize}[leftmargin=0pt, label={}, itemsep=-3pt]
    \item \textbf{Languages:} C, C++, C\#, Python, Java, JavaScript, TypeScript, SQL, Go, Lua, HTML, CSS, Bash
    \item \textbf{Frameworks:} ASP.NET Core, .NET MAUI, Entity Framework, Django, Flask, React, Node.js, Tailwind CSS
    \item \textbf{Databases \& Tools:} PostgreSQL, SQLite, SQL Server, Git, GitHub, Linux, NGINX, Make, GDB, Valgrind, SSH
    \item \textbf{Concepts:} OOP, Data Structures, Algorithms, REST APIs, Design Patterns, Agile, Unit Testing, CI/CD
\end{itemize}

%-------------------------------------------
\end{document}
